\large \bfseries Asymptotic Capacity of Systems with Intelligent Reflective Surfaces

### 2020-07-10 documentation/Presentations/Mid-Presentation/mid_term_presentation.tex
Primary addition is finding multiple roots to the gamma polynomial. Also includes some checks on OFDM implementation

\section{Background}
\begin{frame}
\frametitle{Massive MIMO}
				\centering
		\begin{figure}
		\includegraphics[scale=.18]{Pictures/mimo_antenna}
	\end{figure}
\end{frame}

\begin{frame}
\frametitle{Simplifying the MIMO Channel: OFDM}
Assuming flat-fading channels between each transmit and receive antenna.
	\begin{itemize}
		\item 			
			Interpret each symbol to be the complex coefficient of a complex sinusoid of specific frequency. 
		\item
			These sinusoids pass through a channel whose frequency response is flat.
		\item
			By considering both channel and transmit signal in the frequency domain, we have a system given by
			\begin{equation}
				\my = \mH \mx.
			\end{equation}
		\item 
			Justify if there are any difficulties for OFDM when moving to the high frequencies required for massive MIMO.
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Relay vs. Intelligent Reflective Surface}
\begin{columns}
\begin{column}{0.5\linewidth}
\centering 
	\underline{Relay: Amplify and Forward}
	\\
	\begin{equation*}
	\mathbf{y} = (\mathbf{H}_2\underbrace{\mathbf{F}}_{\text{Relay}}\mathbf{H}_1 + \underbrace{\mathbf{G}}_{\text{LOS}})\mathbf{x}
	\end{equation*}

@@

\begin{frame}
\frametitle{Channel Correlation}
	\begin{itemize}
		\item 
			FIR filters can represent correlation and their AED can be found. (Can just consider subset for FIR length?)
		\item
			The exponential correlation model is one such FIR filter with a single parameter. (Closed form expression for the S-Transform)
		\item 
			Measurement results for similar models show that $\rho$ can take on values up to $.6$ in $x$ GHz (a band relevant to 5G)
	\end{itemize}
\end{frame}

@@

>>>>

\section{Background}
\subsection{MIMO Channel}

\begin{frame}
\frametitle{Massive MIMO}
				\centering
		\begin{figure}
		\includegraphics[scale=.18]{Pictures/mimo_antenna}
	\end{figure}
	\cite{argos2020}
\end{frame}

\begin{frame}
\frametitle{Simplifying the MIMO Channel: OFDM}
Assuming flat-fading channels between each transmit and receive antenna.
	\begin{itemize}
		\item 			
			Interpret each symbol to be the complex coefficient in frequency of a specific complex sinusoid (a sub-carrier). 
		\item
			These sinusoids pass through a channel whose frequency response is flat.
		\item
			By considering both the channel and transmit signals in the frequency domain for each "sub-carrier" in OFDM, we have a system given by
			\begin{equation}
				\vy = \mH \vx.
			\end{equation}
		\item 
			Forms of OFDM are defined for wireless protocols in 5G and 802.11
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Channel Correlation}
	\begin{itemize}
		\item 
			From OFDM perspective this implies correlation between the same sub-carrier at different antennas.
		\item 
			FIR filters can represent some relevant types of correlation.
			Toeplitz can be modeled asymptotically as circulant matrices. AED of circulant matrices is DFT of 1st row
		\item
			The exponential correlation model is one such FIR filter with elements $c_{i,j} = \rho^{i-j} $ with $ 0 \leq \rho \leq 1$.
		\item 
			Measurement results for similar models show that $\rho$ can take on values up to $.6$ in $x$ GHz (a band relevant to 5G)
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Channel Normalization}
\begin{itemize}
\item
	We want to analyze the channel behavior as $N \rightarrow \infty$ without sending capacity to infinity. 
\begin{itemize}
\item
	Normalize the power of the transmitted symbols and channel gains such that $\Expect[\vy^H \vy ] = 1$.
	Enforcing that $\Expect[\vx^H \vx ] = \frac{1}{N}\mathbf{I}$ and $\Expect[\|h_{i,j}\|^2_2 ]= \frac{1}{M}$ for $\mH \in \complex^{M \times N} $ satisfies this.
\end{itemize}
\item
	The popular result that MIMO capacity grows as $\min{N_T, N_R}$ does not include such a normalization. Which type of gain is now eliminated?
\item
	Allows for a matrix to have a converging eigenvalue distribution despite $N, M \rightarrow \infty$.
\end{itemize}
\end{frame}

\subsection{IRS Channel}
\begin{frame}
\frametitle{Relay vs. Intelligent Reflective Surface}
\begin{columns}
\begin{column}{0.5\linewidth}
\centering 
	\underline{Relay: Amplify and Forward}
	\\
	\begin{equation*}
	\mathbf{y} = (\mathbf{H}_2\underbrace{\mathbf{F}}_{\text{Relay}}\mathbf{H}_1 + \underbrace{\mathbf{G}}_{\text{LOS}})\mathbf{x}
	\end{equation*}

@@

@@

\begin{frame}[allowframebreaks]
        \frametitle{References}
        \bibliography{bibliography.bib}
\end{frame}
